Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-14 paper.qmd
Update Figure 6

```{r}
#| label: model-prediction-umap-original

@@

@@

plot_predict_umap_model_connect <- ggplot(data = predict_point_df,
                            aes(
                              x = UMAP1,
                              y = UMAP2, 
                              group = ID
                            )) +
  geom_point(alpha = 0.6) +
  geom_line(alpha = 0.3)
```

```{r}
#| echo: false
#| label: fig-predict-scurve
#| fig-pos: H
#| fig-width: 9
#| fig-height: 5
plot_predict_umap + plot_predict_umap_model + plot_predict_umap_model_connect 
```

<!--prediction for true-model of S-curve-->
::: {#fig-scurve-pred-sc layout-ncol="2" fig-pos="H"}
![](figures/scurve/sc_true_only.png){width="150" fig-align="center"}

![](figures/scurve/pred_true_view.png){width="150" fig-align="center"}

A view of the true model in projections from $7\text{-}D$, and predictions of the true model in \gD{}, for the S-curve data. The predictions fits the UMAP layout which means that it capture the geometry of S-curve with UMAP.
:::

>>>>

<!--prediction for true-model of S-curve-->
```{r}
#| label: model-prediction-umap-original

@@

```{r}
#| label: true-model-projection-langevitour

true_model_df_rm_id <- true_model_df |>
  select(-ID)

projection <- cbind(
    c(0.18390,-0.18443,-0.06860,0.00654,-0.02921,0.02313,-0.08963),
    c(-0.02902,0.03638,-0.16872,0.22418,0.01146,0.02777,0.01453))
projected_df <- as.matrix(true_model_df_rm_id) %*% projection |> 
  as_tibble(.name_repair = "unique") |> 
  rename(c("proj1" = "...1", 
           "proj2" = "...2"))

proj_plot_scurve_true <- ggplot(
  data = projected_df, 
  aes(
    x = proj1, 
    y = proj2)) +
    geom_point(alpha = 0.5)   
```

@@

plot_predict_umap_model_connect <- ggplot(data = predict_point_df,
                            aes(
                              x = UMAP1,
                              y = UMAP2, 
                              group = ID
                            )) +
  geom_point(alpha = 0.5) +
  geom_line(alpha = 0.3)
```

```{r}
#| echo: false
#| label: fig-predict-scurve
#| fig-pos: H
#| fig-width: 9
#| fig-height: 5
proj_plot_scurve_true + plot_predict_umap + 
  plot_predict_umap_model + plot_predict_umap_model_connect +
  plot_layout(ncol = 4)
```

<!-- ::: {#fig-scurve-pred-sc layout-ncol="2" fig-pos="H"} -->
<!-- ![](figures/scurve/sc_true_only.png){width="150" fig-align="center"} -->

<!-- ![](figures/scurve/pred_true_view.png){width="150" fig-align="center"} -->

<!-- A view of the true model in projections from $7\text{-}D$, and predictions of the true model in \gD{}, for the S-curve data. The predictions fits the UMAP layout which means that it capture the geometry of S-curve with UMAP. -->
<!-- ::: -->
